Web-based Supplementary Materials for Combinatorial Mixture Models for Single-Cell Assays with Application to Vaccine Studies by Greg Finak, Steve De Rosa, Mario Roederer and Raphael Gottardo

### 2012-07-27 MIMOSA.tex
Updated as per latest recommendations
Enlarged figure 2, put A and B on first Row, and C on second
Added two-sided simulations to figure 3 as C and D
Improved label for Web Figure B
Cleaned up a stale sentence on two-sided simulation.
Removed fisher's combined p-value from multivariate simulations
MArio's paper already referenced.
Clarified simulation results section referencing Web Figure B and Figure 3 more clearly now.

Signed-off-by: Greg Finak <gfinak@fhcrc.org>

\begin{figure}
\centering
\begin{tikzpicture} [auto,node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.29\columnwidth]{Figures/Fluidigm_plot1.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
\node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.29\columnwidth]{Figures/Fluidigm_plot2.pdf}};
\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
\node at (-0.1,1.1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of B] (C) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (baz) {\includegraphics[width=0.29\columnwidth]{Figures/FluidigmFisher.pdf}};
\begin{scope} [x={(baz.south east)},y={(baz.north west)}]
\node at (0,1) [font=\tiny\sffamily] {C} ;
\end{scope}
\end{tikzpicture}
};
\end{tikzpicture}
\caption{Signed posterior probability, difference and log-odds ratio of the proportion of single-cells expressing each gene on a 96x96 Fluidigm array. The posterior probability of response times the sign of the change in expression is shown in A) (red indicates a decrease, green an increase, relative to the control). Columns and rows are clustered based on these signed posterior probabilities. B) The posterior differences in proportion of cells expressing a gene in the stimulated vs. control samples. Rows and columns are ordered as in A) for comparison. The traces show the deviations of each cell from zero. Colors along the columns denote different stimulations (green: CMV pp65 nlv5, red: HIV Gag, orange: HIV Nef, yellow: CMV pp65 tm10). C) Clustering of the signed q-values from Fisher's exact test. Genes selected from Fisher's exact test at the 10\% FDR level. }
\label{fig:fluidigm}
\end{figure}

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
   \begin{tikzpicture} [auto, node distance=0cm]
   \node at (0,0) (A) {
\begin{tikzpicture}
    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_onesided_ROC_5000.pdf}};
    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [right=of A] (B) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_onesided_FDR_5000.pdf}};
    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {B} ;
    \end{scope}
    \end{tikzpicture}
    };
\end{tikzpicture}
   \caption{Comparison of positivity detection methods on data simulated from the one-sided model. Ten simulations were generated at an $N$ of 5,000 total counts using hyper-parameter estimates from real ICS data (IFNg expressing CD4+ T-cells stimulated with ENV-1-PTEG from HVTN065) with a five-fold effect size between responder and non-responder components. A) Average ROC curve over the 10 simulated data sets (N=5,000) D) Average observed and nominal false discovery rate over 10 simulated data sets (N=5,000). Curves are shown for MIMOSA (one-sided), Fisher's exact test, the likelihood ratio test, and log fold-change. Results for the two-sided model and the MIMOSA fit to a model violating model assumptions, as well as other values of N are in Web Figure B.}\label{fig:simulations}
\end{figure}

To assess the sensitivity of the model to deviations from model assumptions, we repeated the simulations with the cell proportions drawn from  truncated normal distributions on $(0,1)$, rather than beta distributions. The means and variances of the truncated normal distributions were set to the maximum likelihood estimates of the beta distributions defined by the $\alpha,\beta$ hyper parameters estimated from the HVTN065 data set (see Web Figure B panels C and D). Even under these departures from the model assumptions, the unconstrained MIMOSA model outperformed Fisher's exact test and performed about as well as the constrained MIMOSA model fit to one-sided data.

@@

Since the Fluidigm data has a limited number of observations (100 cells and 16 samples), we could not look at more than two makers at once. Therefore, we performed simulations in eight dimension to assess the power of the multivariate MIMOSA  model compared to Fisher's exact test on the resulting 2x5 tables, Fisher's exact test performed marginally on each dimension of the data and p-values combined through Fisher's method ($\chi^2=-2\sum_{i=1}^k\log(p_i)$), as well as the likelihood ratio test (Figure~\ref{fig:mvsimulations} A-C). These results show that multivariate MIMOSA has significantly increased power to detect true differences in multivariate data, even with small counts and small effect sizes, and the model is a better fit to the data than other standard approaches tested for analyzing such multivariate count data (Figure~\ref{fig:mvsimulations} B).

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto, node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.4\columnwidth]{Figures/Multivariate_Sims_ROC.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B) {
\begin{tikzpicture}
   \node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.4\columnwidth]{Figures/Multivariate_Sims_FDR.pdf}};
   \begin{scope} [x={(bar.south east)},y={(bar.north west)}]
       \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
\end{tikzpicture}
   \caption{Multivariate simulations from a two-sided model. Ten, eight-dimensional data sets were simulated from a two-sided model with an effect sizes of $2.5\times 10^{-3}$ and $-2.5\times 10^{-3}$ in two of the eight dimensions (N=1,500). Multivariate MIMOSA was compared against Fisher's exact test, the likelihood ratio test, and Fisher's combined p-value (combining Fisher's exact test run marginally on each of the five dimensions). A) Average ROC curves for the competing methods over 10 simulations. B) Average observed and nominal false discovery rate for each method over 10 simulations.}
   \label{fig:mvsimulations}
\end{figure}

@@

Although we used two single-cell assay platforms as motivating examples, our MIMOSA model can be applied to any type of single-cell assay where cells are dichotomized into positive and negative sets, counted and compared across different conditions. In the case of the Fluidigm data, most analysis methods have been focused on identifying differences in the continuous part of the signal ignoring cells that are undetected (\textit{i.e.} the gene is not expressed in the cell), or simply using this information for pre-filtering~\citep{Flatz:2011jb}. The ability of MIMOSA to identify stimulation-specific expression patterns in single-cell gene expression data demonstrates not only the broader utility of the method, but importantly, also demonstrates that biologically relevant signal is present in the proportion of cells expressing each gene under different conditions (Figure~\ref{fig:fluidigm} A-C).

>>>>

\begin{figure}
\centering
\begin{tikzpicture} [auto,node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.4\columnwidth]{Figures/Fluidigm_plot1.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
\node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.4\columnwidth]{Figures/Fluidigm_plot2.pdf}};
\begin{scope} [x={(bar.south east)},y={(bar.north west)}]
\node at (-0.1,1.1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
\node [below=of A] (C) {
\begin{tikzpicture}
\node[anchor=south west, inner sep=0] at (0,0) (baz) {\includegraphics[width=0.4\columnwidth]{Figures/FluidigmFisher.pdf}};
\begin{scope} [x={(baz.south east)},y={(baz.north west)}]
\node at (0,1) [font=\tiny\sffamily] {C} ;
\end{scope}
\end{tikzpicture}
};
\end{tikzpicture}
\caption{Signed posterior probability, difference and log-odds ratio of the proportion of single-cells expressing each gene on a 96x96 Fluidigm array. The posterior probability of response times the sign of the change in expression is shown in A) (red indicates a decrease, green an increase, relative to the control). Columns and rows are clustered based on these signed posterior probabilities. B) The posterior differences in proportion of cells expressing a gene in the stimulated vs. control samples. Rows and columns are ordered as in A) for comparison. The traces show the deviations of each cell from zero. Colors along the columns denote different stimulations (green: CMV pp65 nlv5, red: HIV Gag, orange: HIV Nef, yellow: CMV pp65 tm10). C) Clustering of the signed q-values from Fisher's exact test. Genes selected from Fisher's exact test at the 10\% FDR level. }
\label{fig:fluidigm}
\end{figure}

@@

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
   \begin{tikzpicture} [auto, node distance=0cm]
   \node at (0,0) (A) {
\begin{tikzpicture}
    \node [anchor=south west] at (0,0) (foo) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_onesided_ROC_5000.pdf}};
    \begin{scope}[x={(foo.south east)},y={(foo.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [right=of A] (B) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (bar) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_onesided_FDR_5000.pdf}};
    \begin{scope}[x={(bar.south east)},y={(bar.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {B} ;
    \end{scope}
    \end{tikzpicture}
    };
        \node [below=of A] (C) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_twosided_ROC_5000.pdf}};
    \begin{scope}[x={(c.south east)},y={(c.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node [anchor=south west] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_onesided_FDR_5000.pdf}};
    \begin{scope}[x={(d.south east)},y={(d.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {D} ;
    \end{scope}
    \end{tikzpicture}
    };

\end{tikzpicture}
   \caption{Comparison of positivity detection methods on data simulated from the one-sided and two--sided models. Ten simulations were generated at an $N$ of 5,000 total counts using hyper-parameter estimates from real ICS data (IFNg expressing CD4+ T-cells stimulated with ENV-1-PTEG from HVTN065) with a five-fold effect size between responder and non-responder components. A) Average ROC curve over the 10 simulated data sets (N=5,000), one--sided B) Average observed and nominal false discovery rate over 10 simulated data sets (N=5,000), one--sided. C) Average ROC curves, two--sided model. D) Average observed and nominal FDR, two--sided model. Curves are shown for MIMOSA, Fisher's exact test, the likelihood ratio test, and log fold-change. Results for MIMOSA fit to a model violating model assumptions, as well as other values of N are in Web Figure B.}\label{fig:simulations}
\end{figure}

To assess the sensitivity of the model to deviations from model assumptions, we repeated the simulations with the cell proportions drawn from  truncated normal distributions on $(0,1)$, rather than beta distributions. The means and variances of the truncated normal distributions were set to the maximum likelihood estimates of the beta distributions defined by the $\alpha,\beta$ hyper parameters estimated from the HVTN065 data set (see Web Figure B panels C and D). Even under these departures from the model assumptions, the unconstrained MIMOSA model outperformed Fisher's exact test.

@@

Since the Fluidigm data has a limited number of observations (100 cells and 16 samples), we could not look at more than two makers at once. Therefore, we performed simulations in eight dimension to assess the power of the multivariate MIMOSA  model compared to Fisher's exact test on the resulting 2x5 tables, as well as the likelihood ratio test (Figure~\ref{fig:mvsimulations} A-C). These results show that multivariate MIMOSA has significantly increased power to detect true differences in multivariate data, even with small counts and small effect sizes, and the model is a better fit to the data than other standard approaches tested for analyzing such multivariate count data (Figure~\ref{fig:mvsimulations} B).

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto, node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (foo) {\includegraphics[width=0.4\columnwidth]{Figures/Multivariate_Sims_ROC_rev.pdf}};
\begin{scope} [x={(foo.south east)},y={(foo.north west)}]
    \node at (0,1) [font=\tiny\sffamily] {A} ;
\end{scope}
\end{tikzpicture}
};
\node [right=of A] (B) {
\begin{tikzpicture}
   \node[anchor=south west, inner sep=0] at (0,0) (bar) {\includegraphics[width=0.4\columnwidth]{Figures/Multivariate_Sims_FDR_rev.pdf}};
   \begin{scope} [x={(bar.south east)},y={(bar.north west)}]
       \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
\end{tikzpicture}
};
\end{tikzpicture}
   \caption{Multivariate simulations from a two-sided model. Ten, eight-dimensional data sets were simulated from a two-sided model with an effect sizes of $2.5\times 10^{-3}$ and $-2.5\times 10^{-3}$ in two of the eight dimensions (N=1,500). Multivariate MIMOSA was compared against Fisher's exact test, and the likelihood ratio test. A) Average ROC curves for the competing methods over 10 simulations. B) Average observed and nominal false discovery rate for each method over 10 simulations.}
   \label{fig:mvsimulations}
\end{figure}

@@

Although we used two single-cell assay platforms as motivating examples, our MIMOSA model can be applied to any type of single-cell assay where cells are dichotomized into positive and negative sets, counted and compared across different conditions. In the case of the Fluidigm data, most analysis methods have been focused on identifying differences in the continuous part of the signal ignoring cells that are undetected (\textit{i.e.} the gene is not expressed in the cell), or the information is used for pre-filtering~\citep{Flatz:2011jb}. The ability of MIMOSA to identify stimulation-specific expression patterns in single-cell gene expression data demonstrates not only the broader utility of the method, but importantly, also demonstrates that biologically relevant signal is present in the proportion of cells expressing each gene under different conditions (Figure~\ref{fig:fluidigm} A-C).

### 2012-07-27 WebSupplementaryMaterialMIMOSA.tex
Updated as per latest recommendations
Enlarged figure 2, put A and B on first Row, and C on second
Added two-sided simulations to figure 3 as C and D
Improved label for Web Figure B
Cleaned up a stale sentence on two-sided simulation.
Removed fisher's combined p-value from multivariate simulations
MArio's paper already referenced.
Clarified simulation results section referencing Web Figure B and Figure 3 more clearly now.

Signed-off-by: Greg Finak <gfinak@fhcrc.org>

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
\node at (0,0) (A) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
    \begin{scope} [x={(a.south east)},y={(a.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {A} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of A] (B) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
        \begin{scope} [x={(b.south east)},y={(b.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {B} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [below=of A] (C) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {C} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of B] (D) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {D} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of C] (E) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {E} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of E] (F) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {F} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [below=of E] (G) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_1000.pdf}};
         \begin{scope} [x={(g.south east)},y={(g.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {G} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [below=of F] (H) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_1000.pdf}};
        \begin{scope} [x={(h.south east)},y={(h.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {H} ;
\end{scope}
    \end{tikzpicture}
    };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to two--sided data (A,B,E,F) or to data where model assumptions are violated (C,D,G,H). Two--sided data were simulated from a standard model. A) Average ROC curves and B) average observed vs nominal FDR from 10 simulations with N=5,000, and E-F) N=1,000. Unconstrained MIMOSA fit to two--sided data simulated from a model where the proportions were drawn from a truncated normal distribution over $[0,1]$, rather than a Beta distribution. C) Average ROC curves and D) average observed vs nominal FDR from 10 simulations at N=5,000, and G-H) N=1,000. }
   \label{webfig:simulations_trunc}
\end{figure}
\bibliographystyle{mn2e}
\bibliography{MIMOSA}

>>>>

\begin{figure} %  figure placement: here, top, bottom, or page
   \centering
\begin{tikzpicture} [auto,node distance=0cm]
%\node at (0,0) (A) {
%\begin{tikzpicture}
%    \node[anchor=south west,inner sep=0] at (0,0) (a) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_5000.pdf}};
%    \begin{scope} [x={(a.south east)},y={(a.north west)}]
%        \node at (0,1) [font=\tiny\sffamily] {A} ;
%    \end{scope}
%    \end{tikzpicture}
%    };
%    \node [right=of A] (B) {
%    \begin{tikzpicture}
%    \node[anchor=south west, inner sep=0] at (0,0) (b) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_5000.pdf}};
%        \begin{scope} [x={(b.south east)},y={(b.north west)}]
%        \node at (0,1) [font=\tiny\sffamily] {B} ;
%        \end{scope}
%    \end{tikzpicture}
%    };
    \node at (0,0) (A) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (c) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_5000.pdf}};
         \begin{scope} [x={(c.south east)},y={(c.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {A} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of A] (B) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (d) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_5000.pdf}};
        \begin{scope} [x={(d.south east)},y={(d.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {B} ;
\end{scope}
    \end{tikzpicture}
    };
  \node [below=of A] (C) {
\begin{tikzpicture}
    \node[anchor=south west,inner sep=0] at (0,0) (e) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_ROC_1000.pdf}};
    \begin{scope} [x={(e.south east)},y={(e.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {C} ;
    \end{scope}
    \end{tikzpicture}
    };
    \node [right=of C] (D) {
    \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (f) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Twosided_FDR_1000.pdf}};
        \begin{scope} [x={(f.south east)},y={(f.north west)}]
        \node at (0,1) [font=\tiny\sffamily] {D} ;
        \end{scope}
    \end{tikzpicture}
    };
    \node [below=of C] (E) {
    \begin{tikzpicture}
     \node[anchor=south west,inner sep=0] at (0,0) (g) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_ROC_1000.pdf}};
         \begin{scope} [x={(g.south east)},y={(g.north west)}]
                 \node at (0,1) [font=\tiny\sffamily] {E} ;
	\end{scope}
     \end{tikzpicture}
     };
     \node [right=of E] (F) {
     \begin{tikzpicture}
    \node[anchor=south west, inner sep=0] at (0,0) (h) {\includegraphics[width=0.4\columnwidth]{Figures/Sim_Truncated_FDR_1000.pdf}};
        \begin{scope} [x={(h.south east)},y={(h.north west)}]
            \node at (0,1) [font=\tiny\sffamily] {F} ;
\end{scope}
    \end{tikzpicture}
    };
 \end{tikzpicture}
   \caption{Unconstrained MIMOSA model fit to data from a model violating model assumptions and to two--sided data with small counts. Data was simulated from a model where proportions were sampled from a truncated normal distribution over $[0,1]$ rather than a Beta distribution.  A) The average ROC from 10 simulation with N=5,000 events. B) The average observed and nominal FDR from 10 simulations with N=5,000 events. C) Average ROC for N=1,000 events D) Average observed and nominal FDR for N=1,000 events. MIMOSA fit to two--sided data were simulated from the standard model with N=1,000 events. A) Average ROC curves from 10 simulations and B) average observed vs nominal FDR from 10 simulations.}
   \label{webfig:simulations_trunc}
\end{figure}
\bibliographystyle{mn2e}
\bibliography{MIMOSA}
